|

### 2020-05-18 paper/Manuscript.Rmd

author: #"`r source('authors_yaml.R')`"
  - name: "Caspar J. Van Lissa"
    institution: "1,2"
    orcid: "0000-0002-0808-5024"
    corresponding: yes
    address: "Padualaan 14, 3584CH Utrecht, The Netherlands"
    email: "c.j.vanlissa@uu.nl"
  - name: "Andreas M. Brandmaier"
    institution: "3,4"
    orcid: "0000-0001-8765-6982"
  - name: "Loek Brinkman"
    institution: "2,5"
    orcid: "0000-0003-3997-1173"
  - name: "Aaron Peikert"
    institution: "6"
    orcid: "0000-0001-7813-818X"
  - name: "Barbara M.I. Vreede"
    institution: "7"
    orcid: "0000-0002-5023-4601"

affiliation: #"`r source('affiliation_yaml.R')`"
  - id: "1"
    institution: "Utrecht University faculty of Social and Behavioral Sciences, department of Methodology & Statistics"
  - id: "2"
    institution: "Open Science Community Utrecht"
  - id: "3"
    institution: "Center for Lifespan Psychology, Max Planck Institute for Human Development, Berlin, Germany"
  - id: "4"
    institution: "Max Planck UCL Centre for Computational Psychiatry and Ageing Research, Berlin, Germany and London, UK"
  - id: "5"
    institution: "UMC Utrecht"
  - id: "6"
    institution: "Test"
  - id: "7"
    institution: "University Library Utrecht"

@@

# Introduction
<!--
Barbara:
A trick I learned in collaborative writing with git is to make sure each new sentence is on a new line.
This way, you can effectively use a git diff to see changes in individual sentences instead of having to scour through an entire paragraph.
I'll add this, but only in the paragraphs I've changed, so you do not get inundated with differences!
-->
The (social) sciences are amidst a paradigm shift towards open science. 
Several immediate causes stirred up support for this transition; including several highly publicized cases of scientific fraud [as discussed by @leveltFailingScienceFraudulent2012], increasing awareness of questionable research practices [@johnMeasuringPrevalenceQuestionable2012], and the replication crisis [@shroutPsychologyScienceKnowledge2018].
However, open science is not merely a cure for this crisis - it is also an opportunity [@adolphOpenBehavioralScience2012].
Technological advances enable researchers to more easily conduct reliable, cumulative, collaborative science [@nosekScientificUtopiaOpening2012].
Capitalizing on these advances has the potential to accellerate scientific progress [see also @coyneReplicationInitiativesWill2016].

@@

The TOP-guidelines are primarily geared towards top-down systemic change by journals, funders, and organizations.
However, large organizations are slow to change.
For example, a snapshot of editorial practices indicated that, in 2015, only 3% out of 1151 psychology journals explicitly stated that they accepted replication studies [@martinArePsychologyJournals2017; see also @klebelPeerReviewPreprint2020].
<!-- A more recent preprint reported that many journals do not explicitly state their policies about  klebelPeerReviewPreprint2020 -->
At the same time, there is substantial momentum for grassroots change [@nosekScientificUtopiaOpening2012].
Many individual researchers are willing to adopt best practices for open science, even in the absence of institutional support.
The formation of "Open Science Communities" at universities around the globe illustrates this grassroots movement.
This paper is designed as an instrument for grassroots change, that can help individual scientists to meet the principles of open science.
This workflow can be used regardless of any top-down open science requirements already implemented by journals and institutions, and where such requirements do exist, this workflow will help fulfill them.

@@

## Prerequisites
<!--Barbara: I'm moving up this section and editing it a bit, to introduce more explicitly that worcs was developed for R.-->
WORCS has focused on developing a workflow for R, instead of for SPSS or Python.
<!-- Barbara: same as for Git, I could not find a citation. Maybe cite the website: www.r-project.org -->
Several arguments support the choice to work in R.
First, R and all of it extensions are free and Open Source, and Open Source software should be the tool of choice for open science.
Second, many tools for an open science workflow are already implemented in R.
A vibrant online community exists for R, developing new R methods and packages, and providing support and tutorials for existing ones.
Wrappers in R are often available for tools developed in other programming languages.
<!-- LB: Perhaps give some pointers to learn R (e.g. R4DataScience)-->
Third, at the time of writing, R is the second-most cited statistical software package [@muenchenPopularityDataScience2012], following SPSS, which has no support for any of the open science tools discussed in this paper.
Finally, R is highly interoperable:
Packages are available to load nearly every imaginable filetype, code written in other programming languages [including Python, @allaireMarkdownPythonEngine] can be called from R, and output can be written to many file types, including DOCX and PDF (in APA style), and HTML format.

Working with R is simplified immensely by using the RStudio integrated development engine (IDE) for R.
<!-- Barbara: 
https://support.rstudio.com/hc/en-us/articles/206212048-Citing-RStudio says:
To cite RStudio in publications, you can get the latest citation information by running the command RStudio.Version() in a recent version of RStudio IDE.

I did this, which gave:

  @Manual{,
    title = {RStudio: Integrated Development Environment for R},
    author = {{RStudio Team}},
    organization = {RStudio, Inc.},
    address = {Boston, MA},
    year = {2016},
    url = {http://www.rstudio.com/},
  }
-->
Many of the tools used in WORCS are embedded directly into the user interface of RStudio.
RStudio automates and streamlines many tedious or complicated aspects of working with R, Rmarkdown, and Git/GitHub.
This makes RStudio a comprehensive solution for open science research projects.
Another important feature of RStudio is project management.
A project bundles writing, analyses, data, references, etcetera, into a self-contained folder, that can be uploaded entirely to GitHub and downloaded by future users.
The `worcs` R-package installs a new RStudio project template.
When a new project is initialized from this template, much of the bookkeeping required to set up an open science project is performed automatically.

@@

The second solution is *version control*:
Maintaining an indelible log of every change to all project files. Version control is a near-essential tool for scientific reproducibility, as anyone learns who has had the experience of accidentally deleting a crucial file, or of being unable to reproduce analyses because they ran some analyses interactively instead of using syntax [see also @blischakQuickIntroductionVersion2016].
Many scientists use some form of *implicit* version control; for example, by renaming files after major changes (e.g., "manuscript_final_2.2-2019-10-12.doc"), tracking changes in word processing software, or using cloud hosting services that retain backups of previous versions.
WORCS instead uses the *explicit* version control software "Git". Git tracks changes to files, and stores these changes when the user makes a "commit".
<!--Barbara: I have looked for a way to cite Git but did not find one... Seems good practice especially in this paper as an example to cite all software, but for Git I just cannot find the way. Maybe cite the website: www.git-scm.com -->
Git retains a complete log of all commits, and users can compare changes between different commits, or go back to a previous version of the code (for example, after making a mistake, or to replicate a previous version of the results).
A project version controlled with Git is called a "Repository", or Repo.
It is also possible to prevent some files from being version controlled - such as privacy sensitive data.
The `.gitignore` file is a list of files that should not be version-controlled, and thus exist only on the user's private computer.

@@

## Considering filetypes
A key consideration when developing a research project is what filetypes to use.
A case can be made to use text-based files only (or as much as possible), instead of binary files.
Text-based files can be read by machines and humans alike, without requiring special (licensed) software.
Binary files, such as Word (`.docx`) or SPSS (`.sav`, `.spo`),  must be decoded by software first.
Git is designed to keep track of changes to the content of text-based files.
Each change reflects a word or line of code added or removed.
Binary files, on the other hand, should not be version controlled with Git, as individual changes in the encrypted file are uninterpretable.
Moreover, text-based files are often smaller than binary files, which means they take up less space on cloud hosting services, such as GitHub. Uploading large binary files is frowned upon.
GitHub also allows visitors to peruse text-based files online, and conveniently renders certain filetypes.
For example, GitHub highlights syntax in `.R` and `.Rmd` files, and displays `.csv` files as spreadsheets.

<!--Barbara: Maybe write here something about writing manuscripts on a line-by-line basis, so that version control can keep track of changes more accurately than if a whole paragraph is identified as altered?-->

@@

<!-- LB:  this section comes at a weird place in the flow of the paper. 
Barbara: agreed! I would remove this altogether.-->
Sometimes, open science principles are discussed as a kind of "antidote" to scientific misconduct. Yet these principles also present an opportunity to conduct more reliable research, with fewer mistakes, more convenient collaboration, more effective internal and external collaboration, and the potential for crowd-sourced error correction.

@@

One important impediment to comprehensive citation is the fact that print journals operate with space constraints.
Print journals often discourage comprehensive citation, either actively, or passively by including the reference list in the manuscript word count.
Researchers can overcome this impediment by preparing two versions of the manuscript:
One version with comprehensive citations for online dissemination, and another version for print, with only the essential citations.
The print version should reference the online version, so interested readers can find the comprehensive reference list.
Step 20 of the WORCS procedure suggests uploading the online version to a preprint server.
This is important because most preprint servers - [at least the ones listed by OSF.io](https://help.osf.io/hc/en-us/articles/360019930493-Preprint-FAQs#how_do_i_find_preprints) - are indexed by Google Scholar.
This means that authors will receive credit for cited work; even if they are cited only in the online version.
Moreover, preprint servers ensure that the online version will have a persistent DOI, and will remain reliably accessible, just like the print version.

It is easiest to mark the distinction between essential and non-essential references from the start, instead of going back to cut references prior to publication. Therefore, the `worcs` package distinguishes between the traditional at-symbol (`@`) used to cite a reference, and the "double at"-symbol (`@`), used to cite a non-essential reference. Users can render a manuscript to PDF either with, or without, comprehensive citations.
<!-- Barbara: I see no difference between these two symbols...-->

@@

When data cannot be shared, researchers should aim to safeguard the potential for computational reproducibility and secondary analysis as much as possible.
WORCS uses two solutions to accomplish this goal.
The first solution is publishing a *checksum* of the raw data upon collection.
A checksum is the result of an algorithm applied to a file, and represents the contents of this file in 32-characters.
Any change to the underlying file results in a different checksum. Thus, one can use a checksum to verify that the contents of a file remain unchanged.
If researchers publish the checksum of their raw data, in addition to the complete analysis code, then they can prove to an independent auditer that running the public analysis code on the private dataset with the correct checksum results in the published results of their work.

The second solution is to share a synthetic dataset with similar characteristics to the real data. Synthetic data mimic the level of measurement and (conditional) distributions of the real data. Sharing synthetic data allows any third party to 1) verify that the published code runs, 2) debug the code, and 3) write valid code for alternative analyses. However, it is important to know that complex multivariate relationships present in the real data are often lost in synthetic data. Thus, findings from the real data might not be replicated in the synthetic data, and findings in the synthetic data *should not be substantively interpreted*. Still, sharing synthetic data facilitates data requests from third parties. A third party can write analysis code based on the synthetic data, and send it to the authors who evaluate it on the real data and send back the results. The ["Pull request"](https://help.github.com/en/github/collaborating-with-issues-and-pull-requests/creating-a-pull-request) functionality on GitHub is a particularly user-friendly way to do this.
<!--Barbara: I'm not sure this is the case. Pull requests are useful if someone wants to change or add to a project, but this would not involve a change to an existing project, but rather a new project/analysis with "old" data. I would remove this suggestion altogether.-->

@@

<!--Barbara: Is it indeed the case that data by default is loaded as a .csv? How about (raw) text data; can worcs accommodate a .txt file, for instance (in case of text analysis)? Or should this all be done in prepare_data.R?-->

@@

Lindsay and colleagues [-@lindsayResearchPreregistration1012016] define preregistration as "creating a permanent record of your study plans before you look at the data. The plan is stored in a date-stamped, uneditable file in a secure online archive." Two such archives are well-known in the social sciences: AsPredicted.org, and OSF.io. However, GitHub also conforms to these standards. Thus, it is possible to preregister a study simply by pushing a text document with the study plans to GitHub. If the GitHub repository is Public, the preregistration is immediately visible to the world, and Reviewers can submit comments through pull requests. If the repository is Private, Reviewers can be invited as "Collaborators", although this removes their anonymity. Private repositories can be made public at a later date, along with their entire time-stamped history. 
<!-- Barbara: Pull requests are not anonymous either, aren't they?-->

@@

The ideal preregistered analysis consists of a complete analysis script that can be evaluated once the data are obtained.
This ideal is often unattainable, because the data present researchers with unanticipated challenges; e.g., assumptions are violated, or analyses work differently than expected.
Some of these challenges can be avoided by simulating the data one expects to obtain, and writing the analysis syntax based on the simulated data.
This topic is beyond the scope of the present paper, but many user-friendly methods for simulating data are available in `R`, including the package [`simstudy`](https://cran.r-project.org/web/packages/simstudy/vignettes/simstudy.html).
<!-- citation:

  @Manual{,
    title = {simstudy: Simulation of Study Data},
    author = {Keith Goldfeld},
    year = {2020},
    note = {R package version 0.1.16},
    url = {https://CRAN.R-project.org/package=simstudy},
  }
  -->
When using the WORCS-workflow, it is recommended to preregister, if possible, a `.R` script with the planned analyses, along with a verbal, conceptual description.
If any changes must be made to the R-script after obtaining the data, one can refer to the conceptual description to explain why these changes are necessary.

@@

Before you can use the WORCS workflow, you have to install the required software, and register for a GitHub account.The setup process is documented in a vignette included with the `worcs` R-package, and also [available online](https://cjvanlissa.github.io/worcs/articles/setup.html). After preparing your system, you can follow the step-by-step procedure outlined below.
<!--Barbara: Does this work on gitlab/bitbucket as well?-->

@@

1. Create a new Private repository on GitHub.
<!-- Why private!?! I would actually argue for a public repo, but if you do not feel comfortable doing so: another option would be to give an overview of advantages/disadvantages of private/public here, and make an argument for either case.-->
Do not change any of the default options. Copy the repository link to the clipboard. This link will look like https://github.com/yourname/yourrepo.git
2. In RStudio, click File > New Project > New directory > WORCS Project Template
    a. Paste the GitHub Repository address in the textbox
    b. Keep the checkbox for `renv` checked if you want to document all dependencies (recommended). The only reason not to do this is if you have dependencies outside of the R environment, or if you are using a more comprehensive solution for computational reproducibility, e.g., @peikertReproducibleDataAnalysis2019.
    c. Select a preregistration template
    d. Click Open in new session, and Create project
3. Write the preregistration `preregistration.Rmd`
4. In the top-right corner of RStudio, select the Git tab, select the checkboxes next to all files, and click the Commit button. Write an informative message for the commit, e.g., "Preregistration", again click Commit, and then click the green Push arrow to send your commit to GitHub
5. Go to the GitHub repository for this project, and tag the Commit as a preregistration
6. Optional: Render the preregistration to PDF, and upload it to AsPredicted.org or OSF.io as an attachment
7. Optional: Add study Materials (only those to which you own the rights!) to the repository.
It is possible to solicit feedback (by opening a GitHub Issue) and receive outside contributions (by accepting Pull requests)
<!-- Barbara: NB this can only be done in a public repo; another argument for making a repo public! -->

@@

8. Read the data into R, and document this procedure in `prepare_data.R`
9. Use `open_data()` or `closed_data()` to store the data
10. Write the manuscript in `Manuscript.Rmd`, using code chunks to perform the analyses.
11. Regularly commit your progress to the Git repository; ideally, after completing each small and clearly defined task. Use informative commit messages. Push the commits to GitHub.
12. Cite essential references with one at-symbol (`[@essentialref2020]`), and non-essential references with a double at-symbol (`[@nonessential2020]`).
<!-- Barbara: Again I cannot see the difference... -->

@@

>>>>

author:
  - name: "Caspar J. Van Lissa"
    institution: "1,2"
    corresponding: yes
    address: "Padualaan 14, 3584CH Utrecht, The Netherlands"
    email: "c.j.vanlissa@uu.nl"
  - name: "Andreas M. Brandmaier"
    institution: "3,4"
  - name: "Loek Brinkman"
    institution: "2,5"
  - name: "Aaron Peikert"
    institution: "3,6"
  - name: "Barbara Vreede"
    institution: "7"

affiliation:
  - id: "1"
    institution: "Utrecht University faculty of Social and Behavioral Sciences, department of Methodology & Statistics"
  - id: "2"
    institution: "Open Science Community Utrecht"
  - id: "3"
    institution: "Center for Lifespan Psychology, Max Planck Institute for Human Development, Berlin, Germany"
  - id: "4"
    institution: "Max Planck UCL Centre for Computational Psychiatry and Ageing Research, Berlin, Germany and London, UK"
  - id: "5"
    institution: "UMC Utrecht"
  - id: "6"
    institution: "Humboldt-Universitaet zu Berlin"
  - id: "7"
    institution: "University Library Utrecht"

@@

# Introduction

The social sciences are amidst a paradigm shift towards open science. Several immediate causes stirred up support for this transition; including several highly publicized cases of scientific fraud [as discussed by @leveltFailingScienceFraudulent2012], increasing awareness of questionable research practices [@johnMeasuringPrevalenceQuestionable2012], and the replication crisis [@shroutPsychologyScienceKnowledge2018]. However, open science is not merely a cure for this crisis - it is also an opportunity [@adolphOpenBehavioralScience2012]. Technological advances enable researchers to more easily conduct reliable, cumulative, collaborative science [@nosekScientificUtopiaOpening2012]. Capitalizing on these advances has the potential to accellerate scientific progress [see also @coyneReplicationInitiativesWill2016].

@@

The TOP-guidelines are primarily geared towards top-down systemic change (what's in a name) by journals, funders, and organizations. However, large organizations are slow to change. For example, a snapshot of editorial practices indicated that, in 2015, only 3% out of 1151 psychology journals explicitly stated that they accepted replication studies [@martinArePsychologyJournals2017; see also @klebelPeerReviewPreprint2020].
<!-- A more recent preprint reported that many journals do not explicitly state their policies about  klebelPeerReviewPreprint2020 --> At the same time, there is substantial momentum for grassroots change [@nosekScientificUtopiaOpening2012]. Many individual researchers are willing to adopt best practices for open science, even in the absence of institutional support. The formation of "Open Science Communities" at universities around the globe illustrates this grassroots movement. This paper is designed as an instrument for grassroots change, that can help individual scientists to meet the principles of open science. This workflow can be used regardless of any top-down open science requirements already implemented by journals and institutions: If such requirements exist, this workflow will help fulfill them.

@@

@@

The second solution is *version control*: Maintaining an indelible log of every change to all project files. Version control is a near-essential tool for scientific reproducibility, as anyone learns who has had the experience of accidentally deleting a crucial file, or of being unable to reproduce analyses because they ran some analyses interactively instead of using syntax [see also @blischakQuickIntroductionVersion2016]. Many scientists use some form of *implicit* version control; for example, by renaming files after major changes (e.g., "manuscript_final_2.2-2019-10-12.doc"), tracking changes in word processing software, or using cloud hosting services that retain backups of previous versions. WORCS instead uses the *explicit* version control software "Git". Git tracks changes to files, and stores these changes when the user makes a "commit". Git retains a complete log of all commits, and users can compare changes between different commits, or go back to a previous version of the code (for example, after making a mistake, or to replicate a previous version of the results). A project version controlled with Git is called a "Repository", or Repo. It is also possible to prevent some files from being version controlled - such as privacy sensitive data. The `.gitignore` file is a list of files that should not be version-controlled, and thus exist only on the user's private computer.

@@

## Additional considerations

A few additional considerations were considered in developing WORCS. The first consideration is to develop a workflow for R, instead of for SPSS or Python. Several arguments support the choice to work in R. First, R and all of it extensions are free and Open Source, and Open Source software should be the tool of choice for open science. Second, all of the aforementioned tools for an open science workflow are already implemented in R. Many statistical methods are first implemented in R, as there is a vibrant online community developing new R-packages and providing support and tutorials for existing ones. Wrappers in R are often available for tools developed in other programming languages. <!-- LB: Perhaps give some pointers to learn R (e.g. R4DataScience)-->Third, at the time of writing, R is the second-most cited statistical software package [@muenchenPopularityDataScience2012], following SPSS, which has no support for any of the open science tools discussed in this paper. Finally, R is highly interoperable: Packages are available to load nearly every imaginable filetype, code written in other programming languages [including Python, @allaireMarkdownPythonEngine] can be called from R, and output can be written to many file types, including DOCX and PDF (in APA style), and HTML format.

Working with R is simplified immensely by using the RStudio user interface for R. Many of the tools used in WORCS are embedded directly into the visual user interface of RStudio. RStudio automates and streamlines many tedious or complicated aspects of working with R, Rmarkdown, and Git/GitHub. This makes RStudio a comprehensive solution for open science research projects. Another important feature of RStudio is project management. A project bundles writing, analyses, data, references, etcetera, into a self-contained folder, that can be uploaded entirely to GitHub and downloaded by future users. The `worcs` R-package installs a new RStudio project template. When a new project is initialized from this template, much of the bookkeeping required to set up an open science project is performed automatically.

Another key consideration is what filetypes to use. A case can be made to use text-based files only (or as much as possible), instead of binary files. Text-based files can be read by machines and humans alike, without requiring special (licensed) software. Binary files, such as Word (`.docx`) or SPSS (`.sav`, `.spo`),  must be decoded by software first. Git is designed to keep track of changes to the content of text-based files. Each change reflects a word or line of code added or removed. Binary files, on the other hand, should not be version controlled. The changes in the encrypted file are uninterpretable. Moreover, text-based files are often smaller than binary files, which means they take up less space on cloud hosting services, such as GitHub. Uploading large binary files is frowned upon. GitHub also allows visitors to peruse text-based files online, and conveniently renders certain filetypes. For example, GitHub highlights syntax in `.R` and `.Rmd` files, and displays `.csv` files as spreadsheets.

@@

<!-- LB:  this section comes at a weird place in the flow of the paper. -->Sometimes, open science principles are discussed as a kind of "antidote" to scientific misconduct. Yet these principles also present an opportunity to conduct more reliable research, with fewer mistakes, more convenient collaboration, more effective internal and external collaboration, and the potential for crowd-sourced error correction.

@@

One important impediment to comprehensive citation is the fact that print journals operate with space constraints. Print journals often discourage comprehensive citation, either actively, or passively by including the reference list in the manuscript word count. Researchers can overcome this impediment by preparing two versions of the manuscript: One version with comprehensive citations for online dissemination, and another version for print, with only the essential citations. The print version should reference the online version, so interested readers can find the comprehensive reference list. Step 20 of the WORCS procedure suggests uploading the online version to a preprint server. This is important because most preprint servers - [at least the ones hosted by OSF.io](https://help.osf.io/hc/en-us/articles/360019930493-Preprint-FAQs#how_do_i_find_preprints) - are indexed by Google Scholar. This means that authors will receive credit for cited work; even if they are cited only in the online version. Moreover, preprint servers ensure that the online version will have a persistent DOI, and will remain reliably accessible, just like the print version.

It is easiest to mark the distinction between essential and non-essential references from the start, instead of going back to cut references prior to publication. Therefore, the `worcs` package distinguishes between the traditional at-symbol (`@`) used to cite a reference, and the "double at"-symbol (`@`), used to cite a non-essential reference. Users can render a manuscript to PDF either with, or without, comprehensive citations.

@@

When data cannot be shared, researchers should aim to safeguard the potential for computational reproducibility and secondary analysis as much as possible. WORCS uses two solutions to accomplish this goal. The first solution is publishing a *checksum* of the raw data upon collection. A checksum represents the contents of a file in a 32-character summary. Any change to the underlying file results in a different checksum. Thus, one can use a checksum to verify that the contents of a file remain unchanged. If researchers publish the checksum of their raw data and the complete analysis code, then they can prove to an independent auditer that running the public analysis code on the private dataset with the correct checksum results in the published results of their work.

The second solution is to share a synthetic dataset with similar characteristics to the real data. Synthetic data mimic the level of measurement and (conditional) distributions of the real data. Sharing synthetic data allows any third party to 1) verify that the published code runs, 2) debug the code, and 3) write valid code for alternative analyses. However, it is important to know that complex multivariate relationships present in the real data are often lost in synthetic data. Thus, findings from the real data might not be replicated in the synthetic data, and findings in the synthetic data *should not be substantively interpreted*. Still, sharing synthetic data facilitates data requests from third parties. A third party can write analysis code based on the synthetic data, and send it to the authors who evaluate it on the real data and send back the results. The ["Pull request"](https://help.github.com/en/github/collaborating-with-issues-and-pull-requests/creating-a-pull-request) functionality on GitHub is a particularly user-friendly way to do this.

@@

@@

Lindsay and colleagues [-@lindsayResearchPreregistration1012016] define preregistration as "creating a permanent record of your study plans before you look at the data. The plan is stored in a date-stamped, uneditable file in a secure online archive." Two such archives are well-known in the social sciences: AsPredicted.org, and OSF.io. However, GitHub also conforms to these standards. Thus, it is possible to preregister a study simply by pushing a text document with the study plans to GitHub. If the GitHub repository is Public, the preregistration is immediately visible to the world, and Reviewers can submit comments through pull requests. If the repository is Private, Reviewers can be invited as "Collaborators", although this removes their anonymity. Private repositories can be made public at a later date, along with their entire time-stamped history.

@@

The ideal preregistered analysis consists of a complete analysis script that can be evaluated once the data are obtained. This ideal is often unattainable, because the data present researchers with unanticipated challenges; e.g., assumptions are violated, or analyses work differently than expected. Some of these challenges can be avoided by simulating the data one expects to obtain, and writing the analysis syntax based on the simulated data. This topic is beyond the scope of the present paper, but many user-friendly methods for simulating data are available in `R`, including the package [`simstudy`](https://cran.r-project.org/web/packages/simstudy/vignettes/simstudy.html). When using the WORCS-workflow, it is recommended to preregister, if possible, a `.R` script with the planned analyses, along with a verbal, conceptual description. If any changes must be made to the R-script after obtaining the data, one can refer to the conceptual description to explain why these changes are necessary.

@@

Before you can use the WORCS workflow, you have to install the required software, and register for a GitHub account. The setup process is documented in a vignette included with the `worcs` R-package, and also [available online](https://cjvanlissa.github.io/worcs/articles/setup.html). After preparing your system, you can follow the step-by-step procedure outlined below.

@@

1. Create a new Private repository on GitHub. Do not change any of the default options. Copy the repository link to the clipboard. This link will look like https://github.com/yourname/yourrepo.git
2. In RStudio, click File > New Project > New directory > WORCS Project Template
    a. Paste the GitHub Repository address in the textbox
    b. Keep the checkbox for `renv` checked if you want to document all R-package dependencies, and have them automatically loaded on any system (recommended).
    c. Select a preregistration template
    d. Click Open in new session, and Create project
3. Write the preregistration `preregistration.Rmd`
4. In the top-right corner of RStudio, select the Git tab, select the checkboxes next to all files, and click the Commit button. Write an informative message for the commit, e.g., "Preregistration", again click Commit, and then click the green Push arrow to send your commit to GitHub
5. Go to the GitHub repository for this project, and tag the Commit as a preregistration
6. Optional: Render the preregistration to PDF, and upload it to AsPredicted.org or OSF.io as an attachment
7. Optional: Add study Materials (to which you own the rights) to the repository. It is possible to solicit feedback (by opening a GitHub Issue) and acknowledge outside contributions (by accepting Pull requests)

@@

8. Read the data into R, and document this procedure in `prepare_data.R`
9. Use `open_data()` or `closed_data()` to store the data
10. Write the manuscript in `Manuscript.Rmd`, using code chunks to perform the analyses.
11. Regularly commit your progress to the Git repository; ideally, after completing each small and clearly defined task. Use informative commit messages. Push the commits to GitHub.
12. Cite essential references with one at-symbol (`[@essentialref2020]`), and non-essential references with a double at-symbol (`[@nonessential2020]`).

@@

## Outlook

<!-- not sure where this repro integration section belongs -->
The `worcs`-package integrates several reproducibility tools into a convenient workflow by assuming reasonable standards that fulfil most researches needs. Currently, however, if a researcher prefers to use other tools that are conceptually similar, they have to leave WORCS behind. We currently integrate WORCS into a modular framework of reproducibility tools for R [@repro], which will serve as the backend for WORCS. This ongoing integration into a unifying framework does not compromise the ease of use for the researcher. However, it gives them more flexibility to satisfy the demands of their research projects while meeting the TOP-guidelines.
